\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-23 paper/experiments.tex
Update query in paper

\section{Experiments}
To evaluate the performance of our approach,  we implemented
a prototype system in Java, following a traditional iterator model.
For our experiments we plan and execute queries
for two separate survey-based data sets, showing that our system
is ideal for early dataset exploration.

@@

Queries 1-5 are on the CDC data. In Query~\ref{q1}, we calculate the average height for users based on their income data. In Query~\ref{q2},
we compare cholesterol levels for individuals at either tail of the income
spectrum and above a certain weight. In Query~\ref{q3},
we extract the maximum blood lead levels for children under the age of 6 years. In Query ~\ref{q4}, we calculate the average systolic blood pressure, by gender, for subjects with a body mass index indicating obesity. In Query ~\ref{q5}, we extract the age (in months), creatine level, and head circumference, for subjects with high creatine levels.

% Perhaps more school makes your head bigger :)

Queries 6-10 are on the FCC data. In Query~\ref{q6}, we calculate the average income for survey participants,
based on their bootcamp attendance. In Query~\ref{q7} estimates the average
age of women from the United States who participated. In Query~\ref{q8}, we 
calculate the average amount of money survey participants with student debt destined to
learning based on their school degree. In Query~\ref{q9}, we join the FCC data with a reference table provided
by the World Bank which summarizes GDP per Capita across various
countries\cite{worldbank-data}. The query calculates the average GDP-per-capita for participants based on whether or not they
attended a bootcamp. Finally, in Query ~\ref{q10}, we identify individuals from countries with GDP per-capita of \$5000 or
less who earn \$100,000 or more post-bootcamp.

@@

%\todobox{actually run experiments and rewrite this section}{
All experiments were run on a single AWS EC2 c4.xlarge instance, with 4 2.9 GHz Intel Xeon E5-2666 v3 virtual CPUs and 7.5 GiB of main memory on Debian Linux.

@@

\begin{figure}
\begin{lstlisting}
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
\caption{A simple aggregate query on ACS data. Imputing the base table is undesirable (did not terminate within 20min). \ProjectName's
quality-optimized and performance-optimized query execute in 9 seconds and 1 second, respectively.
}%TODO MJS
\label{query-acs}
\end{figure}

>>>>

\section{Experiments}\label{sec:experiments}
To evaluate the performance of our approach,  we implemented
a prototype system in Java, following a traditional iterator model.
For our experiments we plan and execute queries
for two separate survey-based data sets, showing that our system
is ideal for early dataset exploration.

@@

Queries 1-5 are on the CDC data. In Query~\ref{q1}, we calculate the average height for
users based on their income data. In Query~\ref{q2}, we compare cholesterol levels for
individuals with low, medium, and high incomes spectrum and above a certain weight. In
Query~\ref{q3}, we extract the maximum blood lead levels for children under the age of 6
years. In Query~\ref{q4}, we calculate the average systolic blood pressure, by gender, for
subjects with a body mass index indicating obesity. In Query~\ref{q5}, we extract the age,
gender, triglyceride levels, and waist circumference from individuals with high triglyceride
levels.

Queries 6-10 are on the FCC data. In Query~\ref{q6}, we calculate the average income for
survey participants, based on their bootcamp attendance. In Query~\ref{q7} estimates the
average age of women from the United States who participated. In Query~\ref{q8}, we
calculate the average amount of money survey participants with student debt destined to
learning based on their school degree. In Query~\ref{q9}, we join the FCC data with a
reference table provided by the World Bank which summarizes GDP per-capita across various
countries\cite{worldbank-data}. The query calculates the average GDP per-capita for
participants based on whether or not they attended a bootcamp. Finally, in Query~\ref{q10},
we identify individuals from countries with GDP per-capita of \$5000 or less who earn
\$100,000 or more post-bootcamp.

@@

%\todobox{actually run experiments and rewrite this section}{
All experiments were run on a single Amazon Web Services EC2 {\tt c4.xlarge} instance, with
four 2.9 GHz Intel Xeon E5-2666 v3 virtual CPUs and 7.5 GiB of main memory, on Debian Linux.

@@

\begin{figure}
\begin{lstlisting}
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
\caption{A simple aggregate query on ACS data. Imputing the base table is prohibitive.
    \ProjectName's quality-optimized and performance-optimized
    query execute in 9 seconds and 1 second, respectively.
}%TODO MJS
\label{query-acs}
\end{figure}
